## odin.js

[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![Travis-CI Build Status](https://travis-ci.org/mrc-ide/odin.js.svg?branch=master)](https://travis-ci.org/mrc-ide/odin.js)
[![AppVeyor Build status](https://ci.appveyor.com/api/projects/status/7o66jpuibiy6havb?svg=true)](https://ci.appveyor.com/project/richfitz/odin-js)
[![codecov.io](https://codecov.io/github/mrc-ide/odin.js/coverage.svg?branch=master)](https://codecov.io/github/mrc-ide/odin.js?branch=master)

```{r, echo = FALSE, results = "hide"}
knitr::opts_chunk$set(error = FALSE)
```

Support for compiling [odin](https://github.com/mrc-ide/odin) models to javascript.

### Use from R

The function `odin.js::odin_js` provides a (roughly drop-in) replacement for `odin::odin` for compiling an odin model for use within R:

```{r}
logistic <- odin.js::odin_js({
  deriv(N) <- r * N * (1 - N / K)
  initial(N) <- N0
  N0 <- user(1)
  K <- 100
  r <- user()
})
logistic
logistic(r = 1)$run(0:10)
```

This might be slightly faster than the odin-to-R compiler, though benchmarks will have to wait until `odin.js` supports more odin features.

### Use from webpages

The function `odin.js::odin_js_bundle` generates a "bundle" of javascript suitable for calling from a webpage.  This is the same code that `odin.js::odin_js` but without R-wrappers around it.  It takes a vector of filenames and produces a file of javascript code:

```{r}
path <- odin.js::odin_js_bundle("inst/models/logistic.R",
                                include_dopri = FALSE)
```

The file at `path` now contains:

```{r, echo = FALSE, results = "asis"}
cat(c("```js", readLines(path), "```"), sep = "\n")
```

(the option `include_dopri` prevents the [`dopri-js`](https://github.com/mrc-ide/dopri-js) solver being included here as that can be included separately and ends up being ~500 lines of extra code).

### Complete example

A more complete example that can actually be used from a webpage is included:

```{r}
path <- odin.js::odin_js_example("inst/models/sir.R", "simple")
dir(path)
```

Chrome will not let you execute js directly off disk (though I think Firefox does) so to test this you should use something like [SimpleHttpServer](https://docs.python.org/2/library/simplehttpserver.html) to serve the directory and access that way.

### Supported features

- [x] user variables
- [ ] output
- [ ] arrays
- [ ] delays
- [ ] interpolation
- [ ] discrete models
- [ ] stochastic models (this might be hard)

---

Please note that the 'odin.js' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
